To Do List

### 2020-09-30 BMC_Genome_Biology_submission/cover_letter_Genome_Biology.Rmd
Formatted for GB
Submitted

---
output:
  pdf_document: default
  html_document: default
  word_document:
    reference_docx: ../Manuscript/styles.doc/NSF_grant_style.docx
---

@@

>>>>

---
output:
  word_document:
    reference_docx: ../Manuscript/styles.doc/NSF_grant_style.docx
  html_document: default
  pdf_document: default
---

September 30, 2020

@@

From: "BioMed Central Editorial Office" <em@editorialmanager.com>
Subject: [EXTERNAL] Confirmation of your submission to Genome Biology GBIO-D-20-01545
Date: September 30, 2020 at 9:04:06 AM EDT
To: "Mikhail G Dozmorov" <mikhail.dozmorov@vcuhealth.org>
Reply-To: "BioMed Central Editorial Office" <editorial@genomebiology.com>

GBIO-D-20-01545 
preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution
Spiro Stilianoudakis; Mikhail G Dozmorov, Ph.D.
Genome Biology

Dear Dr. Dozmorov,

Thank you for submitting your manuscript 'preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution' to Genome Biology.

The submission id is: GBIO-D-20-01545
Please refer to this number in any future correspondence.

During the review process, you can keep track of the status of your manuscript by accessing the following website:

https://urldefense.com/v3/__https://www.editorialmanager.com/gbio/__;!!JqxBPMk!xwmo-1zdQADscZxt7BYRNTr10BgiwyWHUtyM5IrjPB7IhwenePPD6G33cjdQIs2vUCjOuw$

If you have forgotten your username or password please use the "Send Login Details" link to get your login information. For security reasons, your password will be reset.

Best wishes,

Editorial Office
BioMed Central
